Enrich the datasets with new columns.

### 2020-08-27 inst/analysis/analysis_stable.Rmd
Environments

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "analysisStable.tex"), prefix="", default=TRUE)

packages_filepath <- EVALS_SUM_PKGS_FILE
core_filepath <- EVALS_SUM_CORE_FILE
```

@@

We remove a few columns we do not need here and deduplicate.
```{r deduplicate}
eval_calls <- eval_calls_raw %>% count(across(-c(builtin:indirect_allocation)), name = "nb_ev_calls2") %>%
    mutate(nb_ev_calls = nb_ev_calls * nb_ev_calls2) %>% 
    select(-nb_ev_calls2)
```

@@

```{r default_environment}
default_envir <- eval_calls %>% filter(is.na(envir_expression)) 
nb_default_envir <- default_envir %>% count(wt = nb_ev_calls)
nb_call_sites_default_envir <- nb_eval_call_sites(default_envir)
```

`r ratio(nb_default_envir, nb_eval_calls)`% of the calls use the default environment, which corresponds to `r ratio(nb_call_sites_default_envir, nb_call_sites)`% of the call sites.

@@

```{r environment_hierarchy}
# classified_envir <- eval_calls %>% filter(!is.na(envir_expression)) %>%
#       mutate(env_class = pmap(list(environment_class, envir_type, envir_expression), extract_envir)) %>%
#       unnest_wider(env_class)

#TODO
```

>>>>

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
theme_update(text = element_text(size = 20))

create_tags(path(TAGS_DIR, "analysisStable.tex"), prefix="", default=TRUE)

# Temp 
# RUN_DIR   <- path(params$base_dir, "run")
# RUN_TRACE_DIR  <- path(RUN_DIR, "package-evals-traced")
# EVALS_RAW_FILE           <- path(RUN_TRACE_DIR, "raws.fst")
# EVALS_SUM_CORE_FILE      <- path(RUN_TRACE_DIR, "summarized-core.fst")
# EVALS_SUM_PKGS_FILE      <- path(RUN_TRACE_DIR, "summarized-packages.fst")
# EVALS_SUM_KAGGLE_FILE    <- path(RUN_TRACE_DIR, "summarized-kaggle.fst")
# EVALS_SUM_EXTERNALS_FILE <- path(RUN_TRACE_DIR, "summarized-externals.fst")
packages_filepath <- EVALS_SUM_PKGS_FILE
core_filepath <- EVALS_SUM_CORE_FILE
```

@@

We remove a few columns we do not need here and deduplicate.
```{r deduplicate}
# eval_calls <- eval_calls_raw %>% count(across(-c(builtin:indirect_allocation)), name = "nb_ev_calls2") %>%
#     mutate(nb_ev_calls = nb_ev_calls * nb_ev_calls2) %>% 
#     select(-nb_ev_calls2)

#
eval_calls <- eval_calls_raw
```

@@

```{r default_environment}
default_envir <- eval_calls %>% filter(is.na(envir_expression)) 
nb_default_envir <- default_envir %>% count(wt = nb_ev_calls)
nb_call_sites_default_envir <- nb_eval_call_sites(default_envir)

r("default envir expr", nb_default_envir$n)
r("default envir expr percent", ratio(nb_default_envir$n, nb_eval_calls))
r("default envir  call sites percent", ratio(nb_call_sites_default_envir, nb_call_sites))
```

`r ratio(nb_default_envir$n, nb_eval_calls)`% of the calls use the default environment, which corresponds to `r ratio(nb_call_sites_default_envir, nb_call_sites)`% of the call sites.

@@

```{r environment_hierarchy}
# classified_envir <- eval_calls %>% filter(!is.na(envir_expression)) %>%
#       mutate(env_class = pmap(list(environment_class, envir_type, envir_expression), extract_envir)) %>%
#       hoist(env_class, read_env = 1, write_env = 2, .remove=FALSE) #Quicker when not removing

classified_envir <- eval_calls %>% filter(!is.na(envir_expression)) %>% 
  mutate(env_class = pmap_chr(list(environment_class, envir_type, envir_expression), simplify_envir)) %>% 
  mutate(env_class_read = map_chr(env_class, ~ str_match(., "([^\\+]*)\\+?")[[2]]))
```

```{r envirall}
classified_envir %>% ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class)), weight = nb_ev_calls )) +
  coord_flip() +
  scale_y_log10() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

ggsave(path(PLOT_DIR, "environments.pdf"))
```

```{r envir_read}
classified_envir %>% ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class_read)), weight = nb_ev_calls )) +
  coord_flip() +
  scale_y_log10() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

ggsave(path(PLOT_DIR, "environments-read.pdf"))
```

### 2020-08-27 inst/analysis/corpus-stage2.Rmd
Environments

```{r loading raw data}
corpus_s1_raw     <- read_task_result(CORPUS_S1_DETAILS_FILE)
evals_raw         <- read_task_result(PACKAGE_EVALS_FILE)
coverage_raw      <- read_task_result(PACKAGE_COVERAGE_FILE)
metadata_raw      <- read_task_result(PACKAGE_METADATA_FILE)
functions_raw     <- read_task_result(PACKAGE_FUNCTIONS_FILE)
sloc_raw          <- read_task_result(PACKAGE_SLOC_FILE)
runnable_code_raw <- read_task_result(PACKAGE_RUNNABLE_CODE_FILE)
runs_raw          <- read_task_result(PACKAGE_RUNS_FILE)
trace_runs_raw    <- read_task_result(PACKAGE_TRACE_RUNS_FILE)

@@

```{r process runnable code}
runnable_code <- 
  runnable_code_raw %>%
  filter(language=="R") %>%
  mutate(path=case_when(
    str_starts(filename, "./examples") ~ "examples",
    str_starts(filename, "./tests") ~ "tests",
    str_starts(filename, "./vignettes") ~ "vignettes"
  )) %>%
  group_by(package, path) %>%
  summarise(files=n(), code=sum(code)) %>%
  pivot_wider(
    names_from=path, 
    values_from=c(code, files), 
    values_fill=list(code=0, files=0)
  ) %>%
  # TODO we have old version of tidyr, names_glue is missing, so have to rename manually
  rename(
    runnable_code_examples=code_examples,
    runnable_code_tests=code_tests,
    runnable_code_vignettes=code_vignettes,
    runnable_files_examples=files_examples,
    runnable_files_tests=files_tests,
    runnable_files_vignettes=files_vignettes,
  ) %>%
  mutate(
    runnable_code=runnable_code_examples+runnable_code_tests+runnable_code_vignettes,
    runnable_files=runnable_files_examples+runnable_files_tests+runnable_files_vignettes
  ) %>%
  select(
    package,
    runnable_code,
    runnable_files,
    everything()
  )
```

@@

### Package runs

```{r process package runs}
runs <-
  runs_raw %>%
  group_by(package) %>%
  summarise(runnable_success=sum(is.na(error)), runnable_error=sum(!is.na(error)), runnable_time=sum(time, na.rm=TRUE)) %>%
  mutate(runnable_rate=runnable_success/(runnable_success+runnable_error))
```

@@

```{r joining data}
corpus_s1 <-
  corpus_s1_raw %>%
  left_join(metadata, by="package") %>%
  left_join(sloc, by="package") %>%
  left_join(functions, by="package") %>%
  left_join(runnable_code, by="package") %>%
  left_join(coverage, by="package") %>%
  left_join(runs, by="package") %>%
  left_join(trace_runs, by="package") %>%
  left_join(trace_log, by="package") %>%
  left_join(evals, by="package")
```

>>>>

```{r loading raw data}
corpus_s1_raw     <- read_task_result(CORPUS_S1_DETAILS_FILE)
evals_raw         <- read_task_result(PACKAGE_EVALS_FILE)
coverage_raw      <- read_task_result(PACKAGE_COVERAGE_FILE)
metadata_raw      <- read_task_result(PACKAGE_METADATA_FILE)
functions_raw     <- read_task_result(PACKAGE_FUNCTIONS_FILE)
sloc_raw          <- read_task_result(PACKAGE_SLOC_FILE)
runnable_code_raw <- read_task_result(PACKAGE_RUNNABLE_CODE_FILE)
trace_runs_raw    <- read_task_result(PACKAGE_TRACE_RUNS_FILE)

@@

```{r process runnable code}
runnable_code <- 
  runnable_code_raw %>%
  filter(language=="R") %>%
  mutate(path=case_when(
    str_starts(filename, "./examples") ~ "examples",
    str_starts(filename, "./tests") ~ "tests",
    str_starts(filename, "./vignettes") ~ "vignettes"
  )) %>%
  group_by(package, path) %>%
  summarise(files=n(), code=sum(code)) %>%
  pivot_wider(
    names_from=path, 
    values_from=c(code, files), 
    values_fill=list(code=0, files=0)
  ) %>%
  # TODO we have old version of tidyr, names_glue is missing, so have to rename manually
  rename(
    runnable_code_examples=code_examples,
#    runnable_code_tests=code_tests,
    runnable_code_vignettes=code_vignettes,
    runnable_files_examples=files_examples,
#    runnable_files_tests=files_tests,
    runnable_files_vignettes=files_vignettes,
  ) %>%
  mutate(
#    runnable_code=runnable_code_examples+runnable_code_tests+runnable_code_vignettes,
#    runnable_files=runnable_files_examples+runnable_files_tests+runnable_files_vignettes
    runnable_code=runnable_code_examples+runnable_code_vignettes,
    runnable_files=runnable_files_examples+runnable_files_vignettes
  ) %>%
  select(
    package,
    runnable_code,
    runnable_files,
    everything()
  )
```

@@

@@

```{r joining data}
corpus_s1 <-
  corpus_s1_raw %>%
  left_join(metadata, by="package") %>%
  left_join(sloc, by="package") %>%
  left_join(functions, by="package") %>%
  left_join(runnable_code, by="package") %>%
  left_join(coverage, by="package") %>%
  left_join(trace_runs, by="package") %>%
  left_join(trace_log, by="package") %>%
  left_join(evals, by="package")
```

### 2020-08-27 inst/analysis/counts.Rmd
Environments

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    base_dir: /home/aviral/projects/revalstudy2
    kaggle_datafile: "summarized-kaggle.fst"
    core_datafile: "summarized-core.fst"
    packages_datafile: "summarized-packages.fst"
---

@@

source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")
create_tags(path("../paper/tag", "counts.tex"), prefix="", default=TRUE)
```

```{r eval=TRUE}
core_data <- read_fst(params$core_datafile)
packages_data <- 
    read_fst(params$packages_datafile) %>%
    mutate(eval_source_type = "package")
kaggle_data <- 
    read_fst(params$kaggle_datafile)
    #mutate(eval_source_type == "core")

all_data <- bind_rows(core_data, packages_data, kaggle_data)
all_data <-
    all_data %>%
    mutate(eval_call_srcref = 
          coalesce(eval_call_srcref, 
                   str_c("missing", "::", caller_package, "::", caller_function)))

@@

r("total file count", total_file_count)
r("no eval file count", no_eval_file_count)
r("no eval file perc", ratio(no_eval_file_count, total_file_count))
r("core eval file count", core_eval_file_count)
r("core eval file perc", ratio(core_eval_file_count, total_file_count))
r("package eval file count", package_eval_file_count)
r("package eval file perc", ratio(package_eval_file_count, total_file_count))
r("all eval file count", all_eval_file_count)
r("all eval file perc", ratio(all_eval_file_count, total_file_count))

@@

```{r callsite-distribution, eval=TRUE}
```{r call-site-table}
eval_callsite_table <-
    package_calls %>%
    mutate(site_count = if_else(site_count <= 10, as.character(site_count), 
                        if_else(site_count <= 50, "11--50",
                        if_else(site_count <= 100, "51--100",
                        if_else(site_count <= 150, "101--150",
                        if_else(site_count <= 200, "151--200",
                        if_else(site_count <= 250, "201--250",
                        if_else(site_count <= 300, "251--300",
                        "> 300")))))))) %>%
    group_by(site_count) %>%
    summarize(package_count = n()) %>%
    ungroup() %>%
    arrange(match(site_count, c(1:10,"11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300")))

@@

```{r core-dependent-own-eval}

```

>>>>

---
title: "Empirical Evaluation of eval in R"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
editor_options: 
  chunk_output_type: console
---

@@

source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")

create_tags(path(TAGS_DIR, "counts.tex"), prefix="", default=TRUE)
```

```{r eval=TRUE}
run_trace_data <- read_fst(PACKAGE_TRACE_RUNS_FILE)
parallel_kaggle_data <- read_fst(KAGGLE_LOG_FILE)

core_data <- read_fst(EVALS_SUM_CORE_FILE)
packages_data <- 
    read_fst(EVALS_SUM_PKGS_FILE) %>%
    mutate(eval_source_type = "package")

# kaggle should be always empty
kaggle_data <- 
    read_fst(EVALS_SUM_KAGGLE_FILE)
    #mutate(eval_source_type == "core")

all_data <- bind_rows(core_data, packages_data, kaggle_data) %>% as_tibble()
all_data <-
    all_data %>%
    mutate(eval_call_srcref = 
          coalesce(eval_call_srcref, 
                   str_c("missing", "::", caller_package, "::", caller_function)))

@@

overview_table(    
  r("total file count", total_file_count),
  r("no eval file count", no_eval_file_count),
  r("no eval file perc", ratio(no_eval_file_count, total_file_count)),
  r("core eval file count", core_eval_file_count),
  r("core eval file perc", ratio(core_eval_file_count, total_file_count)),
  r("package eval file count", package_eval_file_count),
  r("package eval file perc", ratio(package_eval_file_count, total_file_count)),
  r("all eval file count", all_eval_file_count),
  r("all eval file perc", ratio(all_eval_file_count, total_file_count))
)

@@

```{r callsite-distribution, eval=TRUE}
eval_callsite_table <-
    package_calls %>%
    mutate(site_count = if_else(site_count <= 10, as.character(site_count), 
                        if_else(site_count <= 50, "11--50",
                        if_else(site_count <= 100, "51--100",
                        if_else(site_count <= 150, "101--150",
                        if_else(site_count <= 200, "151--200",
                        if_else(site_count <= 250, "201--250",
                        if_else(site_count <= 300, "251--300",
                        "> 300")))))))) %>%
    group_by(site_count) %>%
    summarize(package_count = n()) %>%
    ungroup() %>%
    arrange(match(site_count, c(1:10,"11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300")))

@@

```{r core-dependent-own-eval}
all_data <- bind_rows(core_data, packages_data, kaggle_data) %>%
  as_tibble() %>%
  mutate(
    package=basename(dirname(dirname(file))),
    core_own_dependent=case_when(
      eval_source == "core"  ~ "core",
      eval_source == "base"  ~ "core",
      package == eval_source ~ "own",
      TRUE ~ "dependent"
    )
  )

# TODO - we need to summarize the data better
# all paths must start with this
stopifnot(nrow(filter(all_data, !startsWith(file, "../../run/"))) == 0)
```

```{r}
cran_programs <- read_fst(CRAN_PROGRAMS_FILE) %>% 
  as_tibble() %>%
  filter(success) %>%
  select(file, corpus)

kaggle_programs <- read_fst(KAGGLE_PROGRAMS_FILE) %>% 
  as_tibble() %>%
  filter(success) %>%
  select(file, corpus)

all_programs <- bind_rows(cran_programs, kaggle_programs)
```

How many programs are missing in the summarized data

```{r}
anti_join(all_programs, all_data, by="file")
```

```{r}
all_programs_cod <-
  map_dfr(
    c("core", "own", "dependent"), 
    ~mutate(
      all_programs,
      core_own_dependent=.,
      nb_ev_calls=0
    )
  )

all_data_summary <- 
  all_data %>%
  select(file, core_own_dependent, corpus, nb_ev_calls) %>%
  right_join(all_programs_cod, by=c("file", "corpus", "core_own_dependent")) %>%
  mutate(nb_ev_calls=ifelse(is.na(nb_ev_calls.x), nb_ev_calls.y, nb_ev_calls.x)) %>%
  select(file, core_own_dependent, corpus, nb_ev_calls)

core_own_dependent <-
  all_data_summary %>%
  group_by(file, core_own_dependent) %>%
  summarize(corpus=first(corpus), eval_calls = sum(nb_ev_calls)) %>%
  ungroup()

# %>%
#   group_by(corpus, core_own_dependent) %>%
#   summarize(
#     total_eval_calls = sum(eval_calls),
#     max_eval_calls = max(eval_calls),
#     min_eval_calls = min(eval_calls),
#     avg_eval_calls = mean(eval_calls)
#   )

vars <- expand.grid(corpus=c("cran", "kaggle"), cod=c("core", "own", "dependent"), stringsAsFactors = FALSE)
map2_dfr(vars$corpus, vars$cod, function(crps, cod) {
  print(filter(core_own_dependent, corpus==crps, core_own_dependent==cod))
  rs(paste(crps, cod, "eval calls"), filter(core_own_dependent, corpus==crps, core_own_dependent==cod)$eval_calls)
}) %>%
  overview_table()

# core_own_dependent  %>%
#   group_by(corpus, core_own_dependent) %>%
#   pivot_longer(cols=c(total_eval_calls, max_eval_calls, min_eval_calls, avg_eval_calls))
# 
#   xtable::xtable(align="llrrrr") %>%
#   print(
#     tabular.environment = "tabularx", 
#     width = "\\textwidth",
#     floating=F,
# #    file=fname,
#     include.rownames=F
#   )

# core_own_dependent %>%
# pmap_dfr(function(corpus, core_own_dependent, total_eval_calls, max_eval_calls, min_eval_calls, avg_eval_calls) {
#     r(str_c(corpus, " ", core_own_dependent, " total eval calls"), total_eval_calls)
#     r(str_c(corpus, " ", core_own_dependent, " max eval calls"), max_eval_calls)
#     r(str_c(corpus, " ", core_own_dependent, " min eval calls"), min_eval_calls)
#     r(str_c(corpus, " ", core_own_dependent, " avg eval calls"), avg_eval_calls)
# })
# 
# datatable(core_own_dependent)
# 
#     xtable::xtable(align="lXrrrr") %>%
#     print(
#       tabular.environment = "tabularx", 
#       width = "\\textwidth",
#       floating=F,
#       file=fname,
#       include.rownames=F
#     )
```

### 2020-08-27 inst/analysis/enrich_dataset.Rmd
Environments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

>>>>

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      # record the current time before each chunk
      now <<- Sys.time()
    } else {
      # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res)
    }
  }
}))

knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE,
                      time_it = TRUE)
